Consistent Polyhedral Surrogates via Embedding

### 2021-07-28 notes/top-k.tex
Mostly testing authentication things but small edits too

For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
\begin{lemma}\label{lem:invar-ones}
	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
\end{lemma}
\begin{proof}
	\begin{align*}
	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha \ones  - e_y)_{[i]} \right)_+\\
	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= L^{top-k}(u)_y
	\end{align*}
\end{proof}

@@

\begin{assumption}\label{assum:nonneg}
	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
\end{assumption}
It follows from Lemma~\ref{lem:extra-elts-zero} that $R^{\tt low}$ is representative, and every $u$ satisfying Assumption~\ref{assum:nonneg} is in $R^{\tt low}$ by construction.

@@

\bigskip
\hrule
\bigskip

@@

\begin{proposition}
	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is representative for $L^{top-k}$.
\end{proposition}

@@

\begin{claim}
	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}$. 
\end{claim}
\begin{proof}
	\begin{align*}
	\inprod{L(\hat \Gamma(p))}{p} &=
	\sum_{y \in H_p} L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u) \\
	&= (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}
%	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
%	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
	\end{align*}
\end{proof}

>>>>

For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
\begin{lemma}\label{lem:invar-ones}
	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
\end{lemma}
\begin{proof}
	\begin{align*}
	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k (u + \alpha \ones  - e_y)_{[i]} \right)_+\\
	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+\\
	&= L^{top-k}(u)_y
	\end{align*}
\end{proof}

@@

It follows from construction of $R^{\tt low}$ that we can take $u_{k+1} = \ldots, = u_{[n]} = 0$.

@@

For $u \in \U$, we can write $\inprod{L^{top-k}(u)}{p}$ as follows:
\begin{align*}
L^{top-k}(u)_y &= 1 + \bar u - u_y - \frac 1 k \min(u_y, 1)\\
\inprod{L^{top-k}(u)}{p} &= 1 + \bar u - \inprod{p}{u} - \frac 1 k \inprod{p}{\min(u, \ones)}
\end{align*}

@@

\begin{claim}
	For each $p \in \mathrm{relint}\simplex$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is affine on the set $\{u \in \U \mid $ the top-$k$ elements of $(u - e_y)$ are the same for all $ y \in \Y\}$.
\end{claim}
\begin{proof}
	For $u \in \U$, the loss for any outcome is given by $L^{top-k}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i = 1}^k(u - e_y)_{[i]}\right)$.
	Since this is affine in the first two terms, it is thus affine on any set for which the last sum is composed of the same elements, which is precisely given by the set above.
\end{proof}

\jessie{This is not precise...}
\begin{proposition}
	$\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}$ is the set of vertices of $L^{top-k}$.
\end{proposition}
\begin{proof}
	Any vertex of the loss surface in $\reals^n \cap \U$ is given by the intersection of (at least) $n-1$ affine halfspaces.
	The set of affine halfspaces composing $L^{top-k}$ is precisely those where the top-$k$ elements of $(u - e_y)$ are the same for all $y \in \Y$.
	These sets shift when either (a) one of the $k$ nonzero elements shifts below $1$ or (b) we hit the boundary of $\U$.
	For (a), this is the intersection of the $n$ hyperplanes where \jessie{...}
	When we hit the boundary of $\U$, the vertices are \jessie{...}
\end{proof}

@@

\begin{claim}
	$\inprod{L(\hat \Gamma(p))}{p} = (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}$. 
\end{claim}
\begin{proof}
	\begin{align*}
	\inprod{L(\hat \Gamma(p))}{p} &=
	\sum_{y \in H_p} p_y L(\hat \Gamma(p))_y + \sum_{y \in M_p, B_p} L(\hat \Gamma(p))_y + \sum_{y \in L_p}L(\hat \Gamma(p))_y \\
	&= \sum_{y \in H_p} 0 + \sum_{y \in M_p, B_p} p_y(\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y(1 + \bar u) \\
	&= (1-p_H) \bar u + p_L - \frac{p_M + p_B}{k}
%	&= \sum_{y \in M_p, B_p, L_p} p_y (\bar u - \frac{1}{k}) + \sum_{y \in L_p} p_y \\
%	&= (1-p_H) (\bar u - \frac{1}{k}) + p_L
	\end{align*}
\end{proof}
